Automatic Extraction of JavaScript Formal Semantics from ECMAScript Specifications

### 2019-08-01 icse/compile.tex
edit section 6

\section{ Initial state configuration ( generator ) }

In this section, we describre how to generate initial environment for ECMAScript to run defined semantics. 
We can extract programming language's AST, Parser, and executable algorithm in the specification with minimal human effort.
With these primitives, we can build entire system for evaluating target language.

Initial environment of language is mostly about initialization of builtin types, or entry point of the program, etc.
In our diagram, we categorized these part as language-dependent environment.
For ECMAScript Specification, initial environment consists of the Builtin objects, Intrinsincs, and Algorithm scope. We will describe how to generate each component.

\subsection{Builtin objects}

@@

 \subsection{Intrinsics}

@@

For type-denpendent algorithms, we organized map from algorithm name to function for each type,
 and we insert functions as propertiy of object when such type of object is created.

 \subsubsection{Syntax-dependent algorithm}
For syntax-dependent algorithm, we insert converted functions in AST structure, and add special expression to call AST-dependent algorithm which requires AST Value and algorithm name.
To insert functions, we gather which AST can be applied to a function. Also, to use subAST structure, we passes subAST in function as argument.

>>>>

\section{ Building entire system to evaluate code }

In this section, we will demonstrate how our idea can be implemented to evaluate programming language. Although it is hard to generalize the process because the format of specification or 
environment of the programming language is varying, We shows the possibility to build entire system for evaluating target language with minimal human effort by giving end-to-end example of ECMAScript langauge.

\subsection{Extracting specification}
First step is to collect language specification and extract component that we can process autoamtically. For our target langauge, ECMAScript, has HTML format of specification in their website, and
in the specification they have BNF form of syntax, highly structured algorithm steps, and verbose texts to describe additional environment to evaluating ECMAScript source code.
We get these information by parsing HTML document, and passing these result to our previous moudle to get AST, Parser, and executable algorithms automatically.

Rest part is initial environment of language such as initialization of builtin types, or entry point of the program, etc.

\subsection{Generating initial environment for evaluating}
For ECMAScript Specification, initial environment consists of the Builtin objects, Intrinsincs. We will describe how to generate each component.

\subsubsection{Builtin objects}

@@

 \subsubsection{Intrinsics}

@@

In ECMAScript specification, there are some objects which has similar interface, but they have different algorithms.

For Example, Object Environment Record and Declarative Environment Record is different object in specification, but they have same name of algorithm(i.e. HasBinding(N))

In this case, algorithm is called in context of calling Object(i.e. x.HasBinding(N)). We name it type-dependent algorithm.
For type-denpendent algorithms, we organized map from algorithm name to function for each type,
 and we insert functions as propertiy of object when such type of object is created.

 \subsubsection{Syntax-dependent algorithm}

 Like type-dependent algorithm, there are many AST Value (in specification, it is called Parse Node) which uses same name of algorithm but the content is differnt.
The most frequent example is Evaluation of the AST Value. every Evaluation algorithm has same name, but each algorithm can be applied for specific syntax. We name it syntax-dependent algorithm.
For syntax-dependent algorithm, we insert converted functions in AST structure, and add special expression to call syntax-dependent algorithm which requires AST Value and algorithm name.
We gather which AST can be applied to a function. Also, to use child node of AST, we passes child node of AST to function as argument.
